\LARGE How coexistence mechanisms mediate temporal stability

### 2014-10-08 modelNotes.Rnw
updated document with math for model

\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx, verbatim}
\usepackage{amsmath}
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{authblk}
\textwidth=6.2in
\textheight=8.5in
%\parskip=.3cm
\oddsidemargin=.1in
\evensidemargin=.1in
\headheight=-.3in

@@

\subsection{Temporal storage effect}

>>>>

\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx, verbatim}
\usepackage{amssymb,amsmath}
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{authblk}
\textwidth=6.2in
\textheight=8.5in
%\parskip=.3cm
\oddsidemargin=.1in
\evensidemargin=.1in
\headheight=-.3in

@@

\subsection{Temporal storage effect}
We start with the simple model

\begin{gather}
N_{i,t+1} =N_{i,t} + N_{i,t}b_{i}(E_{t})[c_{i}w_{i}R-m_{i}]\\
R =s-dR-\sum_{i=1}^{n} c_{i}RN_{i}
\end{gather}

where $b_{i}(E_{t})$ is the year-specific biomass conversion rate for species &i&. Following Adler and Drake (2008), we simualated a time series of annual biomass conversion rates for each species by drawing a sequence of correlate-by-species random variates ($E$) from a multivariate normal distribution with mean 0 and a variance-covariance ($\Sigma$) structure of

\[ \Sigma = \left[ \begin{array}{cc}
\sigma^{2}_{E} & \rho\sigma^{2}_{E} \\
\rho\sigma^{2}_{E} & \sigma^{2}_{E} \end{array} \right].\]

For $\Sigma$, the $\sigma^{2}_{E}$ is the variance of $E$ and $\rho$ is the correlation between the two species' annual biomass conversion rates. For environmental variation to promote coexistence, it must be the case that $\rho<1$.

% \begin{align}
% N_{i,t+1}$ = N_{i,t} + N_{i,t}b_{i}(E_{t})(c_{i}w_{i}R-m)\\
% R$ = t
% \end{align}
